---
title: "Beauty R"
output: html_notebook
---

### 03-16-2020

1. Using the `microbenchmark` package to compare the execution time of R expressions

2. `manipulate` function: The manipulate function accepts a plotting expression and a set of controls (e.g. slider , picker , checkbox , or button ) which are used to dynamically change values within the expression. **may not be as useful as interactive ploting packages like `plotly`???**

```{r eval=FALSE}
library(manipulate)
manipulate(
  plot(cars, xlim = c(x.min, x.max)),
  x.min = slider(0,15),
  x.max = slider(15,30))
```


### 03-17-2020

1. Use `apply` to apply function with multiple arguments to dataframe rows

```{r evel=FALSE}

fun_1 <- function(x,arg1,arg2) pass

res <- apply(fun_1,1,function(x) fun_1(x,arg1,arg2))
```

### 03-18-2020

1. convert a string to be a variable name

https://stackoverflow.com/questions/6034655/convert-string-to-a-variable-name

```{r}
## method 1
pn <- "pname"
pv <- 4
do.call("<-",list(pn,pv)) ## quivalent to pname <- 4

## method 2
as.name("pname") ## if you have a variable with name 'pname'
```

2. display full text in r console

https://community.rstudio.com/t/console-text-truncation-in-tibbles/7098

```{r}
c(text) ## when text is truncated in r console
```


### 03-19-2020

1. convert a list of dataframe to one dataframe

https://stackoverflow.com/questions/2851327/convert-a-list-of-data-frames-into-one-data-frame


### 03-20-2020

1. select rows of dataframe based on unqiue value of a certain column

https://stackoverflow.com/questions/25571547/select-unique-values-with-select-function-in-dplyr-library

```{r}
distinct_df = df %>% distinct(field1,.keep_all=TRUE)

df %>% 
  group_by(x,y) %>%
  summarise() %>%
  select(unique.x=x, unique.y=y)
```

2. Name Extraction Recognition with `monkeylearn` package, 300 free quota every month

https://docs.ropensci.org/monkeylearn/articles/monkeylearn_intro.html























